\subsection{Branching}\label{sec:branching}
Unlike CPU cores, GPUs offer no branch prediction nor speculative execution.
When a multiprocessor is given one or more thread blocks to execute, it partitions them into warps (32 parallel threads), and these execute one common instruction at a time.
Threads can diverge at branch statements, however, and the warp will serially execute each branch path taken for all threads (disabling execution per-thread as appropriate); The threads converge when the paths complete \cite{cuda_guide}. This will kill the performance of the GPU if many threads within a warp diverge.

A major source of branching in the smoothing algorithm arises due to different vertices having different numbers of neighbours. The three main loops (calculating worst coords, calculating the new worst coords, and assembling matrices $A$ \& $q$) all revolve around iterating over a vertex's neighbours, and thus each warp will end up executing the loop `\emph{the maximum degree}' times.

We will therefore investigate the following:
\begin{itemize}
  \item \textbf{Minimising branching}
                Minimising the branches by ordering the individual vertices according to the number of neighbours they have. This will reduce branching since in most warps all threads will process vertices with the same degree and only a few unlucky warps having a transition in the number of neighbours will do some unnecessary work.
                For example if the vertices in colour 0 were 1, 4, 6, 7, 10, 12, with vertices 0, 4, 6, 12 having 6 neighbours, 1 and 7 having 5, and 10 having 4, we would re-order them to be 10, 1, 7 0, 4, 6, 12.

  \item \textbf{Removing corner nodes during colouring}
                The smoothing algorithm bypasses any corner nodes and so we can avoid the conditional branch:
                % Don't adjust the indenting on this, verbatim is irritating!
                \begin{verbatim}
  if(isCornerNode(vid)) {
    return;
  }
                \end{verbatim}
                By factoring out corner nodes during the colouring phase, we remove the need for this branch entirely, which would hopefully provide a slight speed up.
\end{itemize}
